Technical Report

### 2018-03-19 fully-abstract-comp/ftlr-proof-cases.tex
change restrict and seta2b instructions to modify a capability in-place, which is easier.
New treatment of H_sigma as non-global.

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
  \dominique{11-3-2018: proving this lemma depends on lemma~\ref{lem:world-fut-purePart} for the higher-order cases.}
\end{lemma}

@@

{\color{DarkGreen}
\dominique{Proposed proof refactoring below:}
First, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
      \dominique{TODO: simplify restrict,seta2b to modify in-place}
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
      \dominique{TODO: simplify restrict,seta2b to modify in-place}
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz
\end{itemize}

@@

@@

\paragraph{Case: $\protect\txjmp{r_1}{r_2}$} 
In the case $\txjmp{r_1}{r_2}$\footnote{$\pcreg$ is a corner case here. It will fail contradicting previous assumption of termination.} was executed, we know that $\Phi_S(r_1)$ and $\Phi_S(r_2)$ either points to two sealed capabilities or a return pointer pair (all other cases result in $\Phi_S \step \failed$ contradicting $\Phi_S\term[i]$). From assumption \ref{item:reg-ass} we know
\[
  \npair[n']{(\Phi_S(r_i), \Phi_T(r_i))} \in \lrv(W_{R,i}) \text{ for $i = 1,2$}
\]
where $W_{R,i}$ are partitions of the partitioning of $W_R$ we get from assumption \ref{item:reg-ass}. From the previous observation w.r.t. $\Phi_S(r_1)$ and $\Phi_S(r_2)$, we know that we are in the "sealed capability case" of $\lrv$. This in particular gives us that
\[
  \begin{array}{l}
    \forall W' \future W_{r,1}, W_o, n'' < n', (c_S,c_T) \in H_\sigma \; \sigma \; W_o \ldotp \\
    \quad \npair[n'']{\Phi_S(r_1),c_S,\Phi_T(r_1),\sealed{\sigma,c_T}} \in \lrexj(W' \oplus W_o) \wedge \dots
  \end{array}
\]
and
\[
  (\Phi_S(r_2), \vsc_{T,2}) \in H_\sigma \; \sigma \; W_{R,2}
\]
where $\Phi_T(r_2) = \sealed{\sigma,\vsc_{T,2}}$.
Now use the former with $W'=W_{R,1}$, $W_o = W_{R,2}$, and $n'' = i-1$ to get
\[
  \npair[i-1]{\Phi_S(r_1),\Phi_S(r_2),\Phi_T(r_1),\Phi_T(r_2)} \in \lrexj(W_{R,1} \oplus W_{R,2}) 
\]
Using $\lrexj$, we want to ``start from'' configuration pair $(\Phi_S,\Phi_T)$ and end up in $(\Phi_S',\Phi_T')$ where
\begin{itemize}
\item $\Phi_S' = \xjumpResult{\Phi_S(r_1)}{\Phi_S(r_2)}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{\Phi_T(r_1)}{\Phi_T(r_2)}{\Phi_T}$
\end{itemize}
so we simply pick the same memory as in $\Phi_S,\Phi_T$ and the same register file but with $r_1$ and $r_2$ cleared if $\Phi(r_i)$ is linear, respectively. Using $W_M$ memory satisfaction follows from assumption \ref{item:mem-ass}. Using $W_R$ with all the ownership of regions owned by $W_{R,i}$, $i =1,2$ stripped, the register-file satisfaction follows from \ref{item:reg-ass}. Finally the $\npair[i-1]{[(\Phi_S(r_1),\Phi_T(r_1)),(\Phi_S(r_2),\Phi_T(r_2))]}\in\lrp(W_{R,1},W_{R,2})$ follows from the $\lrv$ assumption. Finally the consistency of the worlds we use follows easily.

>>>>

\begin{lemma}[non-linear words are pure]
  \label{lem:non-linear-pure}
  If $\npair{(w_1,w_2)} \in \lrv(H_\sigma,W)$ and ($\nonLinear{w_1}$ or $\nonLinear{w_2}$), then
  $\npair{(w_1,w_2)} \in \lrv(H_\sigma,\purePart{W})$.
\end{lemma}

@@

{\color{DarkGreen}
\dominique{Proposed proof refactoring below:}
First, we prove that one of the following holds:
\begin{itemize}
\item $\Phi_S \step \failed$ and $\Phi_T \step\failed$
\item $\Phi_S \step \halted$ and $\Phi_T \step\halted$
\item All of the following hold:
  \begin{itemize}
  \item $\callCond{\Phi_S,r_1,r_2,\aaddr}$
  \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
  \item $\exec{\Phi_S(\pcreg)}$
  \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
  \item TODO: other useful info
  \end{itemize}
\item All of the following hold: (includes simple cases: gettype, geta, getb, gete, getp, getl, lt, plus, minus, that can be handled uniformly)
  \begin{itemize}
  \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
  \item $z \in \ints$
  \end{itemize}
\item All of the following hold: (includes cap-manipulation cases: move, cca, restrict, seta2b, cseal, split, splice, that can be handled mostly uniformly)
  \begin{itemize}
  \item \item $\Phi_S \step \Phi_S'$
  \item $\Phi_T \step \Phi_T'$
  \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r_1\cdots r_k}{w_1\cdots w_k}}\neq \failed$
  \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r_1\cdots r_k}{w_1'\cdots w_k'}} \neq \failed$
  \item One of the following holds:
    \begin{itemize}
    \item (restrict,cca,seta2b) $w_1 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item (restrict,cca,seta2b) $w_1 = \stkptr{\perm,\baddr,\eaddr,\aaddr}$, $w_2 = ((\perm,\lin),\baddr,\eaddr,\aaddr)$, $\Phi_S(r_1) = \stkptr{\perm',\baddr,\eaddr,\aaddr'}$ and $\Phi_T(r_1) = ((\perm',\lin),\baddr,\eaddr,\aaddr')$ and $\perm' \sqsubseteq\perm$,
      $k = 1$
    \item ...
      \end{itemize}
  \end{itemize}
\item Other cases: store, load, jmp, jnz
\end{itemize}

@@

\dominique{Adapt to new treatment of $H_\sigma$ as non-global}

@@

\paragraph{Case: $\protect\txjmp{r_1}{r_2}$} 
\dominique{Adapt to new treatment of $H_\sigma$ as non-global}
In the case $\txjmp{r_1}{r_2}$\footnote{$\pcreg$ is a corner case here. It will fail contradicting previous assumption of termination.} was executed, we know that $\Phi_S(r_1)$ and $\Phi_S(r_2)$ either points to two sealed capabilities or a return pointer pair (all other cases result in $\Phi_S \step \failed$ contradicting $\Phi_S\term[i]$). From assumption \ref{item:reg-ass} we know
\[
  \npair[n']{(\Phi_S(r_i), \Phi_T(r_i))} \in \lrv(W_{R,i}) \text{ for $i = 1,2$}
\]
where $W_{R,i}$ are partitions of the partitioning of $W_R$ we get from assumption \ref{item:reg-ass}. From the previous observation w.r.t. $\Phi_S(r_1)$ and $\Phi_S(r_2)$, we know that we are in the "sealed capability case" of $\lrv$. This in particular gives us that
\[
  \begin{array}{l}
    \forall W' \future W_{r,1}, W_o, n'' < n', (c_S,c_T) \in H_\sigma \; \sigma \; W_o \ldotp \\
    \quad \npair[n'']{\Phi_S(r_1),c_S,\Phi_T(r_1),\sealed{\sigma,c_T}} \in \lrexj(W' \oplus W_o) \wedge \dots
  \end{array}
\]
and
\[
  (\Phi_S(r_2), \vsc_{T,2}) \in H_\sigma \; \sigma \; W_{R,2}
\]
where $\Phi_T(r_2) = \sealed{\sigma,\vsc_{T,2}}$.
Now use the former with $W'=W_{R,1}$, $W_o = W_{R,2}$, and $n'' = i-1$ to get
\[
  \npair[i-1]{\Phi_S(r_1),\Phi_S(r_2),\Phi_T(r_1),\Phi_T(r_2)} \in \lrexj(W_{R,1} \oplus W_{R,2}) 
\]
Using $\lrexj$, we want to ``start from'' configuration pair $(\Phi_S,\Phi_T)$ and end up in $(\Phi_S',\Phi_T')$ where
\begin{itemize}
\item $\Phi_S' = \xjumpResult{\Phi_S(r_1)}{\Phi_S(r_2)}{\Phi_S}$
\item $\Phi_T' = \xjumpResult{\Phi_T(r_1)}{\Phi_T(r_2)}{\Phi_T}$
\end{itemize}
so we simply pick the same memory as in $\Phi_S,\Phi_T$ and the same register file but with $r_1$ and $r_2$ cleared if $\Phi(r_i)$ is linear, respectively. Using $W_M$ memory satisfaction follows from assumption \ref{item:mem-ass}. Using $W_R$ with all the ownership of regions owned by $W_{R,i}$, $i =1,2$ stripped, the register-file satisfaction follows from \ref{item:reg-ass}. Finally the $\npair[i-1]{[(\Phi_S(r_1),\Phi_T(r_1)),(\Phi_S(r_2),\Phi_T(r_2))]}\in\lrp(W_{R,1},W_{R,2})$ follows from the $\lrv$ assumption. Finally the consistency of the worlds we use follows easily.

### 2018-03-19 fully-abstract-comp/technical-report.tex
New treatment of H_sigma as non-global.

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(\activeReg{\pwheap}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{\pwheap}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{\pwheap}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  \pwheap(r).H \; \pwheap(r).s \; \xi^{-1}(R_W(r)) \wedge\\
      \exists R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal} \wedge\\
      \quad \biguplus_{r \in \dom(\activeReg{\pwheap})} R_\var{seal}) \text{ is defined }\\
      \quad \dom(\pwheap(r).H_\sigma \; \pwheap(r).s) = R_\var{seal}(r)
    \end{array}
  \right.
\]
% }

@@

\lau{TODO: Rewrite the other definitions to pass around $H_\sigma$ (if this is how we want to handle seals.)}

@@

where $H_\sigma$ is a function from seals to the set of pairs of sealable capabilities that can be sealed with $\sigma$.
\dominique{16-3-2018: $H_\sigma$ will need to be step-indexed if it mentions (directly or indirectly) the value relation, to ensure well-foundedness of definitions.}
\lau{28-11-2017: Do we want the execute condition for $\rwx$ as we are doing write xor execute?}

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(H_\sigma,W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
%
    % \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    % \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W}\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W}\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

>>>>

\[
  \memSatHeap{ms,\ms_T}{W} \text{ iff } 
  \left\{
    \begin{array}{l}
      \exists R_\ms : \dom(\activeReg{\pwheap}) \fun \MemSeg \times \MemSeg \wedge \\
      \quad \ms_T = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_2(R_\ms(r)) \wedge \\
      \quad \ms = \biguplus_{r \in \dom(\activeReg{\pwheap})} \pi_1(R_\ms(r)) \wedge \\
      \quad \exists R_W : \dom(\activeReg{\pwheap}) \fun \World\ldotp\\
      \qquad W = \oplus_{r \in \dom(\activeReg{\pwheap})} R_W(r) \wedge\\
      \qquad \forall r \in \activeReg{\pwheap}, n' < n \ldotp \\
      \qquad \quad \npair[n']{R_\ms(r)} \in  \pwheap(r).H \; \pwheap(r).s \; \xi^{-1}(R_W(r)) \wedge\\
      \exists R_\var{seal} : \dom(\activeReg{\pwheap}) \fun \powerset{\Seal} \wedge\\
      \quad \biguplus_{r \in \dom(\activeReg{\pwheap})} R_\var{seal}(r)) \text{ is defined }\\
      \quad \dom(\pwheap(r).H_\sigma \; \pwheap(r).s) = R_\var{seal}(r)
    \end{array}
  \right.
\]
% }

@@

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \exists r \in \dom(\pwheap)\ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; s \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \forall \ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand H_\sigma\; s \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]
